\section{Introduction}

The purpose of this project is to analyze sales data in restaurants using synthetic data generated based on real-world POS (Point of Sale) systems and online sales reports. Since a suitable dataset was not found on Kaggle, the project will proceed with generating its own synthetic data. The validity of the data is crucial for both prediction and analysis, so the generated data has been made as realistic as possible by incorporating features such as a custom menu with prices, defined peak hours, and adjusted quantity based on these peak hours.

\subsection{Objective}
\label{subsection:objective}

The project objective has shifted from predicting sales to analyzing sales data to improve sales. To achieve this, the approach will involve conducting a comprehensive analysis of sales data. This includes examining item performance by analyzing total sales quantity and revenue for each item, as well as evaluating sales performance across different categories. Additionally, popular items and categories will be identified based on sales data, allowing for targeted marketing campaigns and promotions.

The analysis will also delve into price point evaluation to investigate the relationship between pricing and sales volume, as well as assessing the impact of bundling items on sales. Furthermore, time-based analysis will be conducted to identify peak sales periods and seasonal variations, enabling adjustments to promotions and offerings accordingly.

Finally, the insights gained from the sales data analysis will inform decisions about inventory management by forecasting demand using historical sales data to optimize inventory levels. By leveraging these findings, the goal is to improve sales through informed pricing, promotion, marketing, and inventory management strategies.

